|

### 2024-08-30 paper/dcpo_demsupport.Rmd

---
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: yes
    latex_engine: xelatex
    pandoc_args: --lua-filter=multiple-bibliographies.lua

>>>>

---
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_md: yes
    toc: no
    number_sections: yes
    latex_engine: xelatex
    pandoc_args: --lua-filter=multiple-bibliographies.lua
